Memory-Efficient Mixed-Precision Implementations for\\Robust Explicit MPC

### 2019-04-10 emsoft-2019/experiments.tex
fixed subsection capitalization
updating sec. 6...

\subsection{End-to-end Robust Controller}
\eva{Use the same symbol for Delta and Eps as used in the technical section.}

@@

For the pendulum problem, the domain of X is bounded in the range $X_{0} \in
(-3.23, 3.23)$ and $X_{1}\in (-1.46, 1.46)$. MATLAB designs a controller with 14
regions and 58 hyperplanes for each combination of delta and $\varepsilon$.
% delta spans the interval from 0.05 to 0.3, while $\varepsilon$ from 0.0006 to 0.0050.  % it's in the table
For the aircraft problem, the domain of X is bounded in the range $X_{0} \in
(-10000, 10000)$, $X_{1}\in (-734, 734)$, $X_{2}\in (-10000, 10000)$ and
$X_{3}\in (-790, 790)$. MATLAB returns a controller with 27 regions and 217
hyperplanes, except when delta=0.30 and $\varepsilon$=0.001 where the controller
has 26 regions and 208 hyperplanes. In general, when the disturbance value
increases, the state domain X shrinks to be robust against a greater
disturbance, or the number of regions reduces.

\eva{Explain why we choose 32 bits uniform as baseline}
\eva{Explain why we don't compare against other tools (resp. the one)}
\autoref{tab:ipd} shows the total number of bits required to implement each
controller using different precision options: uniform 32 bit precision
(`Uni32'), uniform but custom precision (`Uni', chosen precision in parentheses)
and mixed precision (`Mix'). We split the memory requirement into the bits
required for storing F and G and H and K. We show the results for each benchmark
for ten different combinations of delta and $\varepsilon$, varying one while
keeping the other fixed.
For the pendulum, the execution time of the analysis is 10 minutes no matter the
initial values for delta and $\varepsilon$, while for the aircraft it is 36
minutes. \rocco{maybe table for execution times}

@@

\subsection{Scalability}
The benchmark in this experiment is the double integrator, a canonical example
of a second order control system. 
\eva{More details about this + citation}

For this example, we fix the values for Delta to 0.1 and $\varepsilon$ to 0.001,
but we consider also the prediction horizon m, as an input parameter for the
analysis. At design time, the prediction horizon of the controller m models how
many future iterations of the feed-forward system are considered in the
optimization problem (infinite horizon would correspond to the optimal
controller). Note that in this example, the number of regions is highly
correlated with the prediction horizon m of the controller: the number of regions
increases with larger m, and thus also increases the execution time of our analysis.
Even if this is a general behavior, it is not the rule.
\eva{What does the above sentence mean?}

>>>>

\subsection{End-to-End Robust Controller}
\eva{Use the same symbol for Delta and Eps as used in the technical section.}

@@

\Mahmoud{For the inverted pendulum problem depicted in Section \ref{sec:example}, we set  $m=.344$ kg, $b=0.48$ N s/m, $L=1.703$ m and $T_s=0.1$ s. The gain $K$ is selected such the $\bar A$ has poles at $-0.1$ and $-0.5$. Moreover, we select $N=2$, $R=1$ and $Q=Q_F=100\mathbf{\it I}$, where $\mathbf{ \it I}$ denotes the identity matrix of proper size. The aircraft 4-D model is borrowed from \cite{Kapasouris:1998}. Using the gain $K$, the poles of $\bar A$ are placed at $-5$, $-3$, $-1$ and $-2$. The robust MPC problem is solved for $N=2$, $R=\mathbf{\it I}$ and $Q=Q_F=5\mathbf{\it I}$. Note that for both of the examples, matrices $R$, $Q$ and $Q_F$ are selected such that convergrnce to the origin is given more weight comparing to the control effort as long as constraints are satisfied. \\
We use MATLAB and MPT toolbox software (\cite{matlabMPT})  to compute the explicit MPC, while underlying computations rely on YALMIP(\cite{matlabYALMIP}). For the set of $\varepsilon$ and $\delta$ listed in the Table \ref{tab:ipd}, the off-line computed controller consists of $14$ regions with $58$ 2-D hyperplanes in total. Similarly, for the aircraft model MATLAB computed a robust EMPC with $27$ regions and $217$ 4-D hyperplanes. The only exception is when $\delta=0.30$ and $\varepsilon$=0.001 for which, we got $26$ regions having $208$ hyperplanes. In general, we expect that increasing $\delta$ results in shrinking of feasible set size.}

%the feasible domain $X$ is bounded in the range $X_{0} \in
%(-3.23, 3.23)$ and $X_{1}\in (-1.46, 1.46)$. MATLAB designs a controller with 14
%regions and 58 hyperplanes for each combination of delta and $\varepsilon$.
%% delta spans the interval from 0.05 to 0.3, while $\varepsilon$ from 0.0006 to 0.0050.  % it's in the table
%For the aircraft problem, the domain of X is bounded in the range $X_{0} \in
%(-10000, 10000)$, $X_{1}\in (-734, 734)$, $X_{2}\in (-10000, 10000)$ and
%$X_{3}\in (-790, 790)$. MATLAB returns a controller with 27 regions and 217
%hyperplanes, except when delta=0.30 and $\varepsilon$=0.001 where the controller
%has 26 regions and 208 hyperplanes. In general, when the disturbance value
%increases, the state domain X shrinks to be robust against a greater
%disturbance, or the number of regions reduces.

\eva{Explain why we choose 32 bits uniform as baseline}
\eva{Explain why we don't compare against other tools (resp. the one)}
\autoref{tab:ipd} shows the total number of bits required to implement each
controller using different precision options: uniform 32 bit precision
(`Uni32'), uniform but custom precision (`Uni', chosen precision in parentheses)
and mixed precision (`Mix'). We split the memory requirement into the bits
required for storing F and G and H and K. We show the results for each benchmark
for ten different combinations of delta and $\varepsilon$, varying one while
keeping the other fixed.
For the pendulum, the execution time of the whole analysis is 10 minutes no matter the
initial values for delta and $\varepsilon$, while for the aircraft it is 36
minutes. \rocco{maybe table for execution times}

@@

\subsection{Scalability}
\Mahmoud{The goal of experiments in this section is to show that our algorithm works well even for the case that the controller consists of thousands of PWA functions and regions. 
%Using the algorithm described in Section \ref{???}, the minimum number of bits for storing the controller is computed such that $\delta$ and $\varepsilon$ are respected. 
This experiment is different from the end-to-end case in the sense that designing robust EMPC for the error bound $\delta$ is replaced with designing EMPC that might not count for $\delta$. Given an EMPC, one can perform robustness analysis to come up with an input error bound $\delta$ under which the performance specifications are satisfied. From the implementation point of view, this helps us to scale up-to controllers with thousands of regions, skiping the restrictions for designing robust EMPC with longer time horizons. At this point, our algorithm takes $\delta$ (along with a properly selected $\varepsilon$) and produces the optimum mixed precision that results in significant memory save.\\
The benchmark in this experiment is the double integrator, a canonical example
of a second order control system. Following gives the state space descreption for the discrete time version of double integrator
\begin{equation}
x_{k+1}=
\begin{bmatrix}
1 & T_s\\
0& 1	
\end{bmatrix}
x_k+
\begin{bmatrix}
0\\
T_s
\end{bmatrix}u_k
\label{eq:int2_ss}
\end{equation}
where, $T_s=0.1$ is the sample time. The state and input constraints are
\begin{align*}
	\begin{bmatrix}
		-5\\-5
	\end{bmatrix}\leq&
	x_k\leq
	\begin{bmatrix}
	5\\5
	\end{bmatrix}\\
	-1\leq& u_k \leq 1
\end{align*}}
\eva{More details about this + citation}

\Mahmoud{For this example, $\delta$ and $\varepsilon$ are fixed into $0.1$ and $0.001$, respectively. However, by changing the time horizon $N$ we evaluate scalability of our approach for controllers with very large number of regions. Generally, increasing $N$ results in higher number of regions for the output controller. To compute the explicit model predictive controllers for different time horizons, we use MATLAB MPC toolbox.}

%For this example, we fix the values for $\delta$ to $0.1$ and $\varepsilon$ to $0.001$,
%but we consider also the prediction horizon $N$, as an input parameter for the
%analysis. At design time, the prediction horizon of the controller m models how
%many future iterations of the feed-forward system are considered in the
%optimization problem (infinite horizon would correspond to the optimal
%controller). Note that in this example, the number of regions is highly
%correlated with the prediction horizon m of the controller: the number of regions
%increases with larger m, and thus also increases the execution time of our analysis.
%Even if this is a general behavior, it is not the rule.
\eva{What does the above sentence mean?}
